### 2021-04-07 Chapter-3/Chapter-3.tex
Updates from Overleaf

Even for the up-to-date version of OpenSSL, \tool{} still find several
side-channel leakages. Shown in Figure~\ref{fig:unknown_leakage}.
It is a secret-dependent control flow transfers. 
However, as the branch is inside a loop and a bit shift function causes the branch leak different bits from the sensitive buffer.

\begin{figure}[h]
\centering
\begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
while (!BN_is_bit_set(B, shift)) { /* note that 0 < B */
    shift++;
    if (BN_is_odd(X)) {
        if (!BN_uadd(X, X, n))
            goto err;
    }
    ...
    if (!BN_rshift1(X, X))  // It causes the leak severe!
        goto err;
    ...
}
\end{lstlisting}
    \caption{Unknown sensitive secret-dependent branch leaks from function 
             \textsf{int\_bn\_mod\_inverse} in OpenSSL 1.1.1. The function can leak the last digit from big number \textbf{X}. However, the leak is more severe because of the 
             function \textsf{BN\_rshift1}. Each time function \textsf{BN\_rshift1}
             will shift \textbf{X} right by one and places the result in \textbf{X}. Therefore,
             an attacker can infer multiple bits of \textbf{X} by observing the branch at line 3.}
    \label{fig:unknown_leakage}
\end{figure}

@@

\tool{} works on native x86 execution traces. The design, which is very
precise in terms of true leakages compared to other static source code
method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also has
the common limitations of dynamic approaches. \tool{} may only cover part of the code.
Each time we only get one single execution trace. Therefore,
we may neglect some side-channel vulnerabilities not covered by the traces analyzed.
However, this is not a crucial problem for analyzing crypto libraries, because crypto
libraries are designed to have the same code coverage for various inputs. Our
evaluation also confirms the above point. For symmetric encryption, during our
evaluation there is no secret-dependent control-flow transfers. RSA
implementations have several secret-dependent control-flow transfers.
%But after we manually check those leakages cites. We find
Most of them are  %used for
bound checks, which do not leak much information and have negligible effects
on the whole code coverage as well.

>>>>

Even for the up-to-date version of OpenSSL, \tool{} still find several
side-channel leakages. Figure~\ref{chapter3:fig:unknown_leakage} shows an unknown leakage site in OpenSSL 1.1.1. It is a secret-dependent control flow transfers. 
However, as the branch is inside a loop and a bit shift function causes the branch leak different bits from the sensitive buffer.

\begin{figure}[h]
\centering
\begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
while (!BN_is_bit_set(B, shift)) { /* note that 0 < B */
    shift++;
    if (BN_is_odd(X)) {
        if (!BN_uadd(X, X, n))
            goto err;
    }
    ...
    if (!BN_rshift1(X, X))  // It causes the leak severe!
        goto err;
    ...
}
\end{lstlisting}
    \caption{Unknown sensitive secret-dependent branch leaks from function 
             \textsf{int\_bn\_mod\_inverse} in OpenSSL 1.1.1. The function can leak the last digit from big number \textbf{X}. However, the leak is more severe because of the 
             function \textsf{BN\_rshift1}. Each time function \textsf{BN\_rshift1}
             will shift \textbf{X} right by one and places the result in \textbf{X}. Therefore,
             an attacker can infer multiple bits of \textbf{X} by observing the branch at line 3.}
    \label{chapter3:fig:unknown_leakage}
\end{figure}

@@

\tool{} works on native x86 execution traces. The design, which is very precise in terms of true leakages compared to other static source code method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also has the common limitations of dynamic approaches. \tool{} may only cover part of the code. Each time we only get one single execution trace. Therefore, we may neglect some side-channel vulnerabilities not covered by the traces analyzed.However, this is not a crucial problem for analyzing cryptographic libraries, because cryptographic libraries are designed to have the same code coverage for various inputs. Our evaluation also confirms the above point. For symmetric encryption, during our evaluation there is no secret-dependent control-flow transfers. RSA implementations have several secret-dependent control-flow transfers. Most of them are bound checks, which do not leak much information and have negligible effects on the whole code coverage as well.
